Pillar 2- Quick Topic Models

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_model, file = "App/Recommender System/data_topic_models.RDATA")
save(app_model, file = "./Output/app_model.RDATA")
```

>>>>

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_model, file = "App/Recommender System/app_model.RDATA")
save(app_model, file = "./Output/app_model.RDATA")
```
